Covariate analysis of ROSMAP RNASeq

### 2016-09-03 code/Rmd/ROSMAP_RNASeq_Qntl.Rmd
Added markdown for processign ROSMAP FPKM matrix using quantile normalisation

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq (Based on cogdx)')
```

@@

thisFileName <- 'ROSMAP_RNASeq.Rmd'

@@

# To avoid taking log of zero add 1e-4 to the FPKM counts
EXPR <- log2(EXPR+1e-3)
```
`r dim(EXPR)[1]` number of genes and `r dim(EXPR)[2]` number of samples are considered for the analysis

@@

kable(tmp)
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP RNASeq (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq Qntl (Based on cogdx)')
```

@@

thisFileName <- 'ROSMAP_RNASeq_Qntl.Rmd'

@@

# To avoid taking log of zero add 1e-4 to the FPKM counts
EXPR <- log2(EXPR+1e-3)

# Between sample quantile normalisation
EXPR = normalizeBetweenArrays(data.matrix(EXPR), method = 'quantile')
```
`r dim(EXPR)[1]` number of genes and `r dim(EXPR)[2]` number of samples are considered for the analysis

@@

kable(tmp)
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP RNASeq Qntl (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)
